
# Read in

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)


source(paste(home_folder,"readin.R",sep="")) # read in stan fit, samples, observed data
years.sim <- 2025:2080 #Simulated years
t=23 #Number of years on which the model is run (2003-2025)


```


# Posterior estimates (median and 95%CI)

```{r}

summary(fit, pars="phi_a")$summary[, c("50%", "2.5%",  "97.5%")]
summary(fit, pars="phi_pup")$summary[, c("50%", "2.5%",  "97.5%")]

summary(fit, pars="c")$summary[, c("50%", "2.5%",  "97.5%")]

summary(fit, pars="v0")$summary[, c("50%", "2.5%",  "97.5%")]
summary(fit, pars="v5")$summary[, c("50%", "2.5%",  "97.5%")]

summary(fit, pars="S_diag")$summary[, c("50%", "2.5%",  "97.5%")]

```

```{r}
summary(fit, pars="b0min")$summary[, c("50%", "2.5%",  "97.5%")]
summary(fit, pars="b0max")$summary[, c("50%", "2.5%",  "97.5%")]
summary(fit, pars="b0_av")$summary[, c("50%", "2.5%",  "97.5%")]

summary(fit, pars="alpha_sc")$summary[, c("50%", "2.5%",  "97.5%")]
summary(fit, pars="beta")$summary[, c("50%", "2.5%",  "97.5%")]
summary(fit, pars="w")$summary[, c("50%", "2.5%",  "97.5%")]
summary(fit, pars="K")$summary[, c("50%", "2.5%",  "97.5%")]
```


```{r}

summary(fit, pars="mu")$summary[, c("50%", "2.5%",  "97.5%")]
summary(fit, pars="pi_c_mean")$summary[, c("50%", "2.5%",  "97.5%")]
summary(fit, pars="pi_s_mean")$summary[, c("50%", "2.5%",  "97.5%")]
summary(fit, pars="kappa")$summary[, c("50%", "2.5%",  "97.5%")]

```


```{r}
summary(fit, pars="N_tot[1]")$summary[, c("50%", "2.5%",  "97.5%")]
summary(fit, pars="N_tot[23]")$summary[, c("50%", "2.5%",  "97.5%")]
summary(fit, pars="N_tot[24]")$summary[, c("50%", "2.5%",  "97.5%")]

summary(fit, pars="N_tot[19]")$summary[, c("50%", "2.5%",  "97.5%")]

```

# b_0(h) Birth rate at zero denisty as a function of herring quality (Figure 2C)

```{r}
h=seq(from=-2, to=2, length=30)
h_S=h*sd(df_h$BS)+mean(df_h$BS)
h_G=h*sd(df_h$GoB)+mean(df_h$GoB)

w.mean=mean(samples$w)
alpha=samples$alpha
beta=samples$beta
b0min=samples$b0min
b0max=samples$b0max

B0=matrix(ncol=length(h), nrow=length(alpha))
for ( i in 1:(length(alpha))){
  b0=b0min[i]+(b0max[i]-b0min[i])/(1+exp(-(alpha[i]+beta[i]*h)))
  B0[i,]=b0
}

df.B0.q=as.data.frame(t(apply(B0,2, quantile, quantiles)))
colnames(df.B0.q)<-c("lb","md","ub")
df.B0.q$H=as.numeric(rownames(df.B0.q))

p=ggplot(data=df.B0.q) +
  geom_line(aes(x = H,y=md ),linewidth = 1)+
  geom_ribbon(aes(x = H,ymin=lb, ymax=ub), alpha=0.3)+
  
  theme_classic(base_size = font_size) +
  labs(x="Herring mean weight(g)", y="Birt rate at zero denisty", size=12)+
  theme(text = element_text(size=font_size))
p

ggsave(filename= paste(figure_folder, "b0_herring_function.png",sep=""),
       plot=p,   width=8, height=3)
```





#Historical population szie and growth rate (Figure 2B)

```{r}

N.past <- apply(samples$N[idx,,1:(t+1)], c(1,3), sum)
N.past.q<-t(apply(N.past,2, quantile, quantiles))



N.past.df <- data.frame(Scenario = rep(as.factor('Total population size'), nrow(N.past.q)), 
                        year = (2002):2025,
                        lb = c(N.past.q[,1]), 
                        md = c(N.past.q[,2]), 
                        ub = c(N.past.q[,3]))

G=(N.past[,2:(t+1)]/N.past[,1:t]-1)*100
sc=2000
G.q=t(apply(G,2, quantile, quantiles))*sc
G.df <- data.frame(Scenario = rep(as.factor('Growth rate'), nrow(N.past.q)), 
                   year = (2002):2025,
                   lb = c(NA,G.q[,1]), 
                   md = c(NA,G.q[,2]), 
                   ub = c(NA,G.q[,3]))


p=ggplot(rbind(N.past.df, G.df), aes(x=year,fill=Scenario)) +
  geom_line(aes(y=md, color=Scenario), alpha=1,linewidth=0.4)+
  geom_ribbon(aes(ymin=lb, ymax=ub),linetype=1, alpha=0.1)+
  scale_fill_manual("", values=c("Total population size"="red", "Growth rate"="blue"), guide="none") +
  scale_color_manual("", values=c("Total population size"="red", "Growth rate"="blue")) +


  scale_x_continuous(breaks=seq(2000,2025,5)) +
  scale_y_continuous( sec.axis = sec_axis(~ . /sc, name = "Growth rate (%)", breaks=seq(from=0, to=10, length=6)))+
  labs(x='Year', y='Total population size') +
  theme_classic()+
  theme(legend.position = c(0.3,0.7), text = element_text(size=16),legend.background = element_rect(fill="transparent" ,colour = "transparent"))
p

ggsave(filename= paste(figure_folder,"pop_size_sim_bias.png",sep=""),
      plot=p,   width=8, height=3)


quantile(rowMeans(G), quantiles) #Average growth rate

```



# Simulations


## Readin and set

```{r}
source(paste(home_folder,"simulation_setup.R",sep="")) # read in hunting quota, hunting bias and herring quality scenarios
N.full.hunt=read.csv(paste(simulations_folder,"Simulation.csv",sep=""))
N.composition.sim.median=read.csv(paste(simulations_folder,"Simulation_composition.csv",sep=""))
b.df=read.csv(paste(simulations_folder,"Simulation_birth.csv",sep=""))
N.sim.80.bias=read.csv(paste(simulations_folder,"Simulation_2080_hunting_bias.csv",sep=""))
N.sim.80.her=read.csv(paste(simulations_folder,"Simulation_2080_hunting_her.csv",sep=""))
N.sim.80.3600=read.csv(paste(simulations_folder,"Simulation_2080_3600.csv",sep=""))
N.sim.80.4800=read.csv(paste(simulations_folder,"Simulation_2080_4800.csv",sep=""))

#Set up values for plotting

scenario.colors <- c('Historical'='black', 
                     '0'='red', 
                     '2400'='blue', 
                     '3600'='orange', 
                     '4800'='green3',
                     "1311"="cyan3",
                     "3050"="magenta"
                     )

bias.linetype<- c("Historical"=1,
            "Pup"=2,
            "Adult"=3,
            "Male"=4,
            "Female"=5
            )
bias.alpha<- c("Historical"=0.1,
            "Pup"=0,
            "Adult"=0,
            "Male"=0,
             "Female"=0
            )

her.linetype <- c("Historical"=1,
            "Mean of historical"=1,
            "+0.2g/yr"=2,
            "-0.2g/yr"=3,
            "+4g in 2025"=4,
            "-4g in 2025"=5
            )
her.alpha<- c("Historical"=0.1,
              "Mean of historical"=0.1,
            "+0.2g/yr"=0,
            "-0.2g/yr"=0,
            "+4g in 2025"=0,
            "-4g in 2025"=0
            )
```


##Plots



### Demographic comp (Figure 2D)

```{r}
font_size=15
C=c("#ffa1a1","#ff7878","#ff5757","#ff3737", "#fc0000", "#c00", "#a1ddff","#70ccff", "#3fbaff", "#0ea9ff", "#008edc", "#006eab")

t.c=24

# Past compostion
N=as.vector((matrix(summary(fit, pars="N")$summary[,"mean"], ncol=t.c)))
year=seq(from=2002, to=2025, length=24)
df.age.str <- data.frame(group=as.factor(rep(1, 12*t.c)), year=rep(year, 12),
                         GenderAge=rep(c(paste("Female ", c(0:4, "5+")),
                                         c(paste("Male ", c(0:4, "5+")))), each=t.c),
                         count=N)
df.age.str$ratio=with(df.age.str,count/ ave(count, year, FUN=sum) )
year=seq(from=2002, to=2025+length(years.sim.composition), length=23+length(years.sim.composition))

# Simulated composition
N.sim.med= as.vector((as.matrix(N.composition.sim.median)))
df.age.str.sim <- data.frame(group=as.factor(rep(1, 12*length(years.sim.composition))),
                             year=rep(years.sim.composition, 12),
                             GenderAge=rep(c(paste("Female ", c(0:4, "5+")),
                                             c(paste("Male ", c(0:4, "5+")))),
                                           each=length(years.sim.composition)),
                             count=N.sim.med)

df.age.str.sim$ratio=with(df.age.str.sim,count/ ave(count, year, FUN=sum) )
df.age.str.sim$Scenario="Predicted"
df.age.str$Scenario="Historical"


p=ggplot(rbind( df.age.str.sim,df.age.str),aes(x=year, y=ratio, group=GenderAge, fill=GenderAge)) + 
  geom_area(col="black", linewidth=0.3)  +  labs(x = 'Year', y='Relative frequency')+
  scale_fill_manual(values=C,name='Gender and Age') +   
  geom_vline(aes(xintercept=2025), linetype='dotted',linewidth=1,  col="black") +
  scale_alpha_manual(values=c(1, 0.5), name="")+ theme_classic(base_size = font_size)
p

ggsave(filename= paste(figure_folder, "dem_comp.png",sep=""),plot=p,   width=8, height=6)

```

#### Report results
```{r}

 i=3
 for ( i in 1:6){
   print(round(100*(mean(df.age.str[df.age.str$GenderAge== unique(df.age.str$GenderAge)[i],]$ratio))))
   
   print(round(100*(mean(df.age.str[df.age.str$GenderAge== unique(df.age.str$GenderAge)[i+6],]$ratio))))
 }
 
df_60=df.age.str.sim[df.age.str.sim$year==2060,]
for ( i in 1:6){
   print(round(100*(df_60[df_60$GenderAge== unique(df_60$GenderAge)[i],]$ratio)))
               
             print(round(100*(df_60[df_60$GenderAge== unique(df_60$GenderAge)[i+6],]$ratio)))
}
```


### Hunting bias (Figure 3)
```{r}

N.full.hunt.bias=N.full.hunt[N.full.hunt$Herring_quality %in% c("Historical", "Mean of historical"),]
N.full.hunt.bias$group=paste(N.full.hunt.bias$Scenario, N.full.hunt.bias$Hunting_bias)


last.year=years.sim[length(years.sim)]
ymax=220000

breaks=c(-20000,100,20000,40000,60000,80000,100000,120000,140000, 160000,180000,200000, 220000)

breaks.plot=c(100,60000,80000,100000,120000,140000, 160000, 210000)
X=(breaks[1:(length(breaks)-1)]+breaks[2:(length(breaks))])/2

plot=list()

col=c("red","cyan3", "blue",rep("orange",5),  "green3")
T=c(scenario.breaks[2:4], paste(scenario.breaks[5], bias.breaks, sep="\n") , scenario.breaks[6])
ax_lab.size=8
lab.size=3


for ( j in 1:length(B.list)){
  dat=as.numeric(N.sim.80.bias[j,])
  P={}
  P.n={}
  C={}
  len=length(dat)
  if (j==1) {x_ax= breaks.plot}
  else{x_ax=c()}
  for ( i in 1:(length(breaks)-1)){
        P.n[i]=round(((sum(dat>=breaks[i])-sum(dat>breaks[i+1]))/length(dat))*100)
        P[i]=paste(P.n[i], "%")
        if(P.n[i]==0){P[i]=""}
  }
       
  plot[[j]] =
    
    local({
        dat <-dat
        C<- C
        P<-P
        x_ax<-x_ax
        y=max(ggplot_build(ggplot()+geom_histogram(aes(x=dat,y= ..density..), breaks=breaks))$data[[1]]$y)/2
        p1 <-   ggplot() +
  geom_histogram(aes(x =dat,y= ..density..),fill = col[j] , alpha=0.4,col="white", breaks=breaks)+
 # geom_density(aes(x =dat), fill=col[j], alpha=0.1, col="white",adjust=1/2)+
  geom_text(aes(x=(breaks[1:(length(breaks)-1)]+breaks[2:(length(breaks))])/2,label =P,y =y), size=lab.size)+
  coord_flip() +
  theme_classic() +
 
  scale_x_continuous(breaks=x_ax,limits=c(-20000,ymax)) +
  scale_y_continuous(breaks=c(), limit= c(0,y*2)) +
  labs(x="",y="")+
           ggtitle(T[j])+
  theme(legend.position = c(-9,0.2), text = element_text(size=ax_lab.size))+
  scale_fill_identity(name='Carrying capacity', guide='none')+
  theme(plot.margin = margin(t = 10, b = 10, l = 0, r = 10)  )+
              theme(plot.title = element_text(hjust =0.2, vjust=-5))
        print(p1)
    })
  
  
}

p2= 
  plot[[1]]+ theme(plot.title = element_text(hjust =0.2, vjust=0))+
  plot[[2]]+  theme(plot.title = element_text(hjust =0.2, vjust=0))+
  plot[[3]]+ theme(plot.title = element_text(hjust =0.2, vjust=0))+
  plot[[4]]+theme(plot.title = element_text(hjust =0.2, vjust=-4))+
  plot[[5]]+ theme(plot.title = element_text(hjust =0.2, vjust=-4))+
  plot[[6]]+ theme(plot.title = element_text(hjust =0.2, vjust=-4))+
  plot[[7]]+ theme(plot.title = element_text(hjust =0.2, vjust=-4))+
  plot[[8]]+ theme(plot.title = element_text(hjust =0.2, vjust=-4))+

    plot[[9]]+  theme(plot.title = element_text(hjust =0.2, vjust=0))+
    plot_layout(widths =  rep(1,9))
 

p=ggplot(N.full.hunt.bias, aes(x=year, group=group,alpha=Hunting_bias,fill=Scenario,linetype = Hunting_bias)) +
  geom_line(aes(y=md, color=Scenario), alpha=1,linewidth=0.4)+
  geom_ribbon(aes(ymin=lb, ymax=ub),linetype=1) +
  
  scale_fill_manual("", values=scenario.colors, breaks=scenario.breaks, guide="none") +
  scale_linetype_manual("Hunting bias", values=bias.linetype, breaks=bias.breaks) +
  scale_color_manual("Hunted Seals", values=scenario.colors, breaks=scenario.breaks) +
  scale_alpha_manual( values=bias.alpha, breaks=bias.breaks, guide="none") +
  
  scale_x_continuous(breaks=seq(2000,2100,10)) +
  scale_y_continuous(limits = c(0,ymax)) +
  labs(x='Year', y='Total population size') +
  theme_classic()+
  theme(legend.position = c(0.1,0.6), text = element_text(size=10),legend.background = element_rect(fill="transparent" ,colour = "transparent"))
  #ggtitle("Population trajectories")+
 p2+

    plot_layout(widths = c(10,10))
p

ggsave(filename= paste(figure_folder, "pop_size_sim_bias_traj.png",sep=""),
      plot=p,   width=8, height=5)


ggsave(filename= paste(figure_folder, "pop_size_sim_bias_2080.png",sep=""),
      plot=p2,   width=8, height=5)

```

#### Report expected final pop size & surviva probability

```{r}
sc=3600
round(N.full.hunt.bias[N.full.hunt.bias$Scenario==sc & N.full.hunt.bias$year==2080,"lb"])
round(N.full.hunt.bias[N.full.hunt.bias$Scenario==sc & N.full.hunt.bias$year==2080,"md"])
round(N.full.hunt.bias[N.full.hunt.bias$Scenario==sc & N.full.hunt.bias$year==2080,"ub"])

rowSums(N.sim.80.bias[,,]<100)/length(idx)*100 #hist
B.list
```


### Herring quality (Figure 4A)
```{r}
N.full.hunt.her=N.full.hunt[N.full.hunt$Hunting_bias=="Historical",]

N.full.hunt.her$group=paste(N.full.hunt.her$Scenario, N.full.hunt.her$Herring_quality)


last.year=years.sim[length(years.sim)]
ymax=230000
ymax=210000


breaks=c(-3000,2000,60000,80000,100000,120000,140000, 160000, 210000)

breaks.plot=c(0,60000,80000,100000,120000,140000, 160000, 210000)
X=(breaks[1:(length(breaks)-1)]+breaks[2:(length(breaks))])/2

plot=list()
her.breaks.short=c("Mean of hist.",
            "+0.2g/yr",
            "-0.2g/yr",
            "+4g in 2025",
            "-4g in 2025")

col=rep("orange",5)
# T=c(scenario.breaks[2:4], paste(scenario.breaks[5], her.breaks.short, sep="\n") , scenario.breaks[6])

T=c( her.breaks.short)

ax_lab.size=4
lab.size=3


H.list=c(1,2,3,4,5)
for ( j in 1:length(H.list)){
  dat=as.numeric(N.sim.80.her[j,])
  P={}
  P.n={}
  C={}
  len=length(dat)
  if (j==1) {x_ax= breaks.plot}
  else{x_ax=c()}
  for ( i in 1:(length(breaks)-1)){
        P.n[i]=((sum(dat>=breaks[i])-sum(dat>breaks[i+1]))/length(dat))*100
        P[i]=paste(round(P.n[i]), "%")
  }
       
  plot[[j]] =
    
    local({
        dat <-dat
        C<- C
        P<-P
        x_ax<-x_ax
        y=max(ggplot_build(ggplot()+geom_histogram(aes(x=dat,y= ..density..), breaks=breaks))$data[[1]]$y)/2
        p1 <-   ggplot() +
  geom_histogram(aes(x =dat,y= ..density..),fill = col[j] , alpha=0.4,col="white", breaks=breaks)+
  #geom_density(aes(x =dat), fill=col[j], alpha=0.1, col="white",adjust=1/2)+
  geom_text(aes(x=(breaks[1:(length(breaks)-1)]+breaks[2:(length(breaks))])/2,label =P,y =y), size=2)+
  coord_flip() +
  theme_classic() +
 
  scale_x_continuous(breaks=x_ax,limits=c(-3000,ymax)) +
  scale_y_continuous(breaks=c(), limit= c(0,y*2)) +
  labs(x="",y="")+
           ggtitle(T[j])+
  theme(legend.position = c(-9,0.2), text = element_text(size=5))+
  scale_fill_identity(name='Carrying capacity', guide='none')+
  theme(plot.margin = margin(t = 10, b = 10, l = 0, r = 10)  )+
              theme(plot.title = element_text(hjust =0.6, vjust=-5))
        print(p1)
    })
  
  
}

p2= 
  plot[[1]]+ theme(plot.title = element_text(hjust =-0.1, vjust=-2))+
  plot[[2]]+ theme(plot.title = element_text(hjust =0.5, vjust=-2))+
  plot[[3]]+ theme(plot.title = element_text(hjust =0.5, vjust=-2))+
  plot[[4]]+ theme(plot.title = element_text(hjust =0.5, vjust=-2))+
  plot[[5]]+ theme(plot.title = element_text(hjust =0.5, vjust=-2))+

      plot_layout(widths =  rep(1,9))
 

p=ggplot(N.full.hunt.her, aes(x=year, group=group,alpha=Herring_quality,fill=Scenario,linetype = Herring_quality)) +
  geom_line(aes(y=md, color=Scenario), alpha=1,linewidth=0.4)+
  geom_ribbon(aes(ymin=lb, ymax=ub),linetype=1) +
  
  scale_fill_manual("", values=scenario.colors, breaks=scenario.breaks, guide="none") +
  scale_linetype_manual("Herring quality", values=her.linetype, breaks=her.breaks) +
  scale_color_manual("Hunted Seals", values=scenario.colors, breaks=scenario.breaks) +
  scale_alpha_manual( values=her.alpha, breaks=her.breaks, guide="none") +
  
  scale_x_continuous(breaks=seq(2000,2100,10)) +
  scale_y_continuous(limits = c(0,ymax)) +
  labs(x='Year', y='Total population size') +
  theme_classic()+
    ggtitle("Population size in 2080 with 3600 hunted seals")+

  theme(legend.position = c(0.1,0.6), text = element_text(size=10),legend.background = element_rect(fill="transparent" ,colour = "transparent"))+  
  p2+
    plot_layout(widths = c(10,5.55))
ggsave(filename= paste(figure_folder, "pop_size_sim_hers.png",sep=""),
      plot=p,   width=12.44, height=5)
p
```


#### Report expected final pop size & surviva probability

```{r}
sc=3600
N.full.hunt.her[N.full.hunt.her$Scenario==sc & N.full.hunt.her$year==2080,"lb"]
N.full.hunt.her[N.full.hunt.her$Scenario==sc & N.full.hunt.her$year==2080,"md"]
N.full.hunt.her[N.full.hunt.her$Scenario==sc & N.full.hunt.her$year==2080,"ub"]

rowSums(N.sim.80.her<100)/length(idx)*100 #hist

sc=4800

N.full.hunt.her[N.full.hunt.her$Scenario==sc & N.full.hunt.her$year==2057,"md"]

```

####Surival probabilities heatmap (Figure 4B)

```{r}

y=length(years.sim)

colnames(N.sim.80.3600)<- her.breaks
rownames(N.sim.80.3600)<- bias.breaks
N.sim.80.3600=N.sim.80.3600[c("Male","Historical", "Pup", "Adult","Female"),c("Mean of historical" ,        "-0.2g/yr",   "-4g in 2025"  , "+0.2g/yr" , "+4g in 2025")]
p=pheatmap((round(N.sim.80.3600)), treeheight_col = 0,treeheight_row = 0, display_numbers = 100-round((N.sim.80.3600)),
           show_colnames = FALSE,
           cluster_rows = FALSE,
           cluster_cols = FALSE,
          legend = TRUE,
          fontsize = 15,
          number_color = "white" , border_color = "white", color = 
           colorRampPalette(c("red", "gold3", "navy"))(100),
           #hcl.colors(100, "RdYlBu"),
           breaks=seq(from=100, to=0, length=100), main="3600")

ggsave(filename= paste(figure_folder, "surv_prob_3600.png",sep=""),
      plot=p,   width=4.2, height=2.8)

colnames(N.sim.80.4800)<- her.breaks
rownames(N.sim.80.4800)<- bias.breaks

N.sim.80.4800=N.sim.80.4800[c("Male","Historical", "Pup", "Adult","Female"),c("Mean of historical" ,        "-0.2g/yr",   "-4g in 2025"  , "+0.2g/yr" , "+4g in 2025")]
p=pheatmap((round(N.sim.80.4800)), treeheight_col = 0,treeheight_row = 0, display_numbers = 100-round((N.sim.80.4800)),
           show_colnames = TRUE, 
            fontsize = 15,
           cluster_cols = FALSE,
           cluster_rows = FALSE,
          number_color = "white" , border_color = "white", color = 
           colorRampPalette(c("red", "gold3", "navy"))(100),
           #hcl.colors(100, "RdYlBu"),
           breaks=seq(from=0, to=100, length=100), main="4800")
p
ggsave(filename= paste(figure_folder, "surv_prob_4800.png",sep=""),
      plot=p,   width=4.2, height=4)

```



#### Birth (Figure 2A)
```{r}

#Past birth
b.past <- samples$b[idx,]
b.past.q<-t(apply(b.past,2, quantile, quantiles))

b.past.df <- data.frame(Scenario = rep(as.factor('Historical'), nrow(b.past.q)), 
                        year = (2002):2025,
                        lb = c(b.past.q[,1]), 
                        md = c(b.past.q[,2]), 
                        ub = c(b.past.q[,3]))

sc=75
b.past.df$h_S=df_h$BP_GoF/sc
b.past.df$h_G=df_h$GoB/sc

#Simualted birth
#b.df.NA <- data.frame(Scenario = rep(as.factor(her.breaks), each=length(years.sim.birth)), 
                              # year = rep(years.sim.birth, nrow(h_S.scenarios)),
                              # lb = c(t(b[1,,])), 
                              # md = c(t(b[2,,])), 
                              # ub = c(t(b[3,,])))

b.df$h_S=NA
b.df$h_G=NA


her.scenario.colors <- c('Historical'='black', 
                     "Mean of historical" ='red', 
                     "+0.2g/yr"='blue', 
                     "-0.2g/yr"='orange', 
                     "+4g in 2025"='green3',
                     "-4g in 2025"='cyan3'
                     )


b.full.df=rbind(b.past.df, b.df)

p=ggplot(b.full.df, aes(x=year),linewidth=0.4) +
  geom_line(aes(y=md, color=Scenario),  alpha=1)+
  geom_ribbon(aes(ymin=lb, ymax=ub, fill=Scenario), alpha=0.1) +
  geom_line(aes(y=h_S, linetype="Southern Baltic Sea"), col="darkgreen", alpha=0.8)+
  geom_line(aes(y=h_G, linetype ="Gulf of Bothnia"),col="darkgreen", alpha=0.8)+
  #geom_errorbar(aes( ymin=lb_obs, ymax=ub_obs), alpha=0.3) +
  #geom_point(aes( y=b_obs, color='black', size=Total)) +
  scale_color_manual("Herring quality scenarios", values=her.scenario.colors, breaks=her.breaks, guide=guide_legend(ncol=2)) +
  scale_fill_manual(values=her.scenario.colors) +
  scale_size("Sample size of\npregnancy rate data",range = c(0, 4), breaks=c(5,10,15,20))+
  #scale_size_manual("Size",values=c(1,5,10,20), guide=guide_legend(ncol=2)) +
  scale_linetype_manual("Historical herring quality" ,values=c("Southern Baltic Sea"=3,"Gulf of Bothnia"=2), breaks=c("Southern Baltic Sea","Gulf of Bothnia"), guide=guide_legend(ncol=1)) +
  scale_x_continuous(breaks=seq(2000,2100,10)) +
  scale_y_continuous( sec.axis = sec_axis(~ . *sc, name = "Herring weight (g)", breaks=seq(from=33, to=48, length=6)))+
  labs(x='Year', y='Birth rate') +
  guides(color = guide_legend(title.position = "top", ncol=2, order=2),linetype = guide_legend(title.position = "top", ncol=1, order=1), fill="none", size=guide_legend(title.position = "top",ncol=2))+
  theme_classic(base_size = font_size) +
  theme(legend.position = c(0.3,0.14), text = element_text(size=font_size),legend.background = element_rect(fill="transparent" ,colour = "transparent")    ,legend.direction = "vertical", legend.box = "horizontal")


p
ggsave(filename= paste(figure_folder, "birth_sim_num.png",sep=""),
      plot=p,   width=16, height=8)
```

### Hunting fo graphical abstract
```{r}

N.full.hunt.short=N.full.hunt[N.full.hunt$Herring_quality %in% c("Historical", "Mean of historical") & N.full.hunt$Hunting_bias=="Historical",]
N.full.hunt.sh$group=paste(N.full.hunt.bias$Scenario, N.full.hunt.bias$Hunting_bias)


last.year=years.sim[length(years.sim)]
ymax=210000



for ( j in 1:length(B.list)){
  dat=as.numeric(N.sim.80.bias[j,])
  P={}
  P.n={}
  C={}
  len=length(dat)
  if (j==1) {x_ax= breaks.plot}
  else{x_ax=c()}
  for ( i in 1:(length(breaks)-1)){
        P.n[i]=round(((sum(dat>=breaks[i])-sum(dat>breaks[i+1]))/length(dat))*100)
        P[i]=paste(P.n[i], "%")
        if(P.n[i]==0){P[i]=""}
  }
       
  plot[[j]] =
    
    local({
        dat <-dat
        C<- C
        P<-P
        x_ax<-x_ax
        y=max(ggplot_build(ggplot()+geom_histogram(aes(x=dat,y= ..density..), breaks=breaks))$data[[1]]$y)/2
        p1 <-   ggplot() +
  geom_histogram(aes(x =dat,y= ..density..),fill = col[j] , alpha=0.4,col="white", breaks=breaks)+
 # geom_density(aes(x =dat), fill=col[j], alpha=0.1, col="white",adjust=1/2)+
  geom_text(aes(x=(breaks[1:(length(breaks)-1)]+breaks[2:(length(breaks))])/2,label =P,y =y), size=lab.size)+
  coord_flip() +
  theme_classic() +
 
  scale_x_continuous(breaks=x_ax,limits=c(-20000,ymax)) +
  scale_y_continuous(breaks=c(), limit= c(0,y*2)) +
  labs(x="",y="")+
           ggtitle(T[j])+
  theme(legend.position = c(-9,0.2), text = element_text(size=ax_lab.size))+
  scale_fill_identity(name='Carrying capacity', guide='none')+
  theme(plot.margin = margin(t = 10, b = 10, l = 0, r = 10)  )+
              theme(plot.title = element_text(hjust =0.2, vjust=-5))
        print(p1)
    })
  
  
}

p2= 
  plot[[1]]+ theme(plot.title = element_text(hjust =0.2, vjust=0))+
  plot[[2]]+  theme(plot.title = element_text(hjust =0.2, vjust=0))+
  plot[[3]]+ theme(plot.title = element_text(hjust =0.2, vjust=0))+
  plot[[4]]+theme(plot.title = element_text(hjust =0.2, vjust=-4))+
  plot[[5]]+ theme(plot.title = element_text(hjust =0.2, vjust=-4))+
  plot[[6]]+ theme(plot.title = element_text(hjust =0.2, vjust=-4))+
  plot[[7]]+ theme(plot.title = element_text(hjust =0.2, vjust=-4))+
  plot[[8]]+ theme(plot.title = element_text(hjust =0.2, vjust=-4))+

    plot[[9]]+  theme(plot.title = element_text(hjust =0.2, vjust=0))+
    plot_layout(widths =  rep(1,9))
 

p=ggplot(N.full.hunt.short, aes(x=year, group=Scenario,alpha=Hunting_bias,fill=Scenario)) +
  geom_line(aes(y=md, color=Scenario), alpha=1,linewidth=1)+
  geom_ribbon(aes(ymin=lb, ymax=ub),linetype=1) +
  
  scale_fill_manual("", values=scenario.colors, breaks=scenario.breaks, guide="none") +
  scale_linetype_manual("Hunting bias", values=bias.linetype, breaks=bias.breaks) +
  scale_color_manual("Hunted Seals", values=scenario.colors, breaks=scenario.breaks) +
  scale_alpha_manual( values=bias.alpha, breaks=bias.breaks, guide="none") +
  
  scale_x_continuous(breaks=seq(2000,2100,10)) +
  scale_y_continuous(limits = c(0,ymax)) +
  labs(x='Year', y='Total population size') +
  theme_classic()+
  theme(legend.position = c(0.2,0.6), text = element_text(size=20),legend.background = element_rect(fill="transparent" ,colour = "transparent"))+
  ggtitle("Simulated population trajectories")
  
  
ggsave(filename= paste(figure_folder, "pop_size_sim_ga.png",sep=""),
      plot=p,   width=9, height=5)

```


```{r}
p=ggplot()+stat_density(aes(x=samples$K, col="Posterior"),geom="line",position="identity")+stat_density(aes(x=rlnorm(10000, 11.3,0.3), col="Prior"),geom="line",position="identity")+scale_color_manual("",values=c("Prior"="blue", "Posterior"="red"))+theme_classic()+xlab("Carrying capacity")+theme(legend.position = c(0.7,0.5), text = element_text(size=ax_lab.size))

ggsave(filename= paste(figure_folder, "Carrying_capacity_posterior_prior.png",sep=""),
      plot=p,   width=9, height=5)

```

