```{r setup, include=FALSE}
library("priorsense")
library(patchwork)

knitr::opts_chunk$set(echo = TRUE)

source(paste(code_folder,"readin.R",sep="")) # read in stan fit, samples, observed data
source(paste(code_folder,"plotting_functions.R",sep="")) # read in stan fit, samples, observed data

```

### Terminology disclaimer

Note, in the code we use "bias" to denote hunting selectivity. The latter term 
is used in the paper. The difference between the paper and code arises from 
the reason that we used the less good "bias" in the original submission.



### Aerial count

```{r}
years=seq(from=2003, to=2024, length=22)
p=pp_raster(samples$y_sim[,2:23], as.vector(years), bin_width=100, years, as.numeric(c(y_obs)), cex=2,
          x_lab='Year', y_lab='Aerial survey count', interpolate = FALSE) +
  guides(fill=guide_colorbar(title.position='top', direction='horizontal'),
         colour=guide_legend(override.aes = list(size=3))) +
  theme(legend.position = c(0.35,0.85), legend.spacing.y = unit(0.05, "cm"), 
        legend.background = element_rect(fill = NA), panel.grid.minor = element_blank(), text = element_text(size=20))
p
ggsave(filename= paste(figure_folder,"post_pred_aerial_count.png",sep=""),plot=p,   width=8, height=5)

```

### Reproductive signs

```{r}

df=read.csv(paste(proc_data_folder,"Herring.csv", sep=""))
years=seq(from=2002, to=2024, length=23)

apply(samples$z_sim, c(2,3), quantile, 0.5)
p.post.q<- apply(samples$p, 2, quantile, quantiles)[,1:23]
b.post.q<- apply(samples$b, 2, quantile, quantiles)[,1:23]
Z.sim.00=samples$z_sim[,1,]
Z.sim.10=samples$z_sim[,2,]
Z.sim.01=samples$z_sim[,3,]
Z.sim.11=samples$z_sim[,4,]
Z.sim.PS=Z.sim.10+Z.sim.11
#Z=Z[,1:22]
Z.sim.CA=Z.sim.01+Z.sim.11
Z.tot=colSums(Z_fi)
Z_CA.sim.q<- apply(t(Z.sim.CA)/Z.tot, 1, quantile, quantiles, na.rm=TRUE)
Z_PS.sim.q<- apply(t(Z.sim.PS)/Z.tot, 1, quantile, quantiles, na.rm=TRUE)

p<-ggplot() +
  geom_ribbon(aes(x=years, ymin=b.post.q[1,], ymax=b.post.q[3,], fill='gray16'), alpha=0.15) +
  geom_line(aes(x=years, y=b.post.q[2,]), col='gray16', alpha=0.5) +

  geom_errorbar(aes(x=years, ymin=Z_PS.sim.q[1,], ymax=Z_PS.sim.q[3,]), alpha=0.35, color="black") +
  geom_linerange(aes(x=years, ymin=Z_PS.sim.q[1,], ymax=Z_PS.sim.q[3,]), color = "black", alpha=0)+
  geom_point(aes(x=years, y=(Z_fi[2,]+Z_fi[4,])/Z.tot,  size=Z.tot), color='black',alpha=1) +
  scale_fill_identity(name='', guide='legend', labels=c('Posterior estimate \n of true value')) +
  scale_size_continuous(name='Sample size', guide='legend') +
  scale_y_continuous(limits=c(0,1)) +
  
  labs(x='Year', y='Proportion with placental scar') +
  theme_classic() +

  theme(panel.grid.minor = element_blank(), text = element_text(size=18), legend.position = c(0.47,0.2), label.position="bottom", legend.direction="horizontal") +
  guides(size=guide_legend(title.position="top", label.position = 'bottom'),
         fill='none')

p 
ggsave(filename= paste(figure_folder,"post_pred_PS.png",sep=""),plot=p,    width=7, height=8)

p<-ggplot() +
  geom_ribbon(aes(x=years, ymin=b.post.q[1,], ymax=b.post.q[3,], fill='gray16'), alpha=0.15) +
  geom_line(aes(x=years, y=b.post.q[2,]), col='gray16', alpha=0.5) +
  
  geom_errorbar(aes(x=years, ymin=Z_CA.sim.q[1,], ymax=Z_CA.sim.q[3,]), alpha=0.35, color="black") +
  geom_linerange(aes(x=years, ymin=Z_CA.sim.q[1,], ymax=Z_CA.sim.q[3,]), color = "black", alpha=0)+
  geom_point(aes(x=years, y=(Z_fi[3,]+Z_fi[4,])/Z.tot, size=Z.tot), color='black', alpha=1) +

  scale_fill_identity(name='', guide='legend', labels=c('Posterior estimate \n of true value')) +
  scale_size_continuous(name='Sample size', guide='legend') +
  scale_y_continuous(limits=c(0,1)) +
  
  labs(x='Year', y='Proportion with CA') +
  theme_classic() +
  theme(panel.grid.minor = element_blank(), text = element_text(size=18), legend.position = c(0.47,0.2), label.position="bottom", legend.direction="horizontal") +
  guides(size=guide_legend(title.position="top", label.position = 'bottom'),
         fill='none')

p
ggsave(filename= paste(figure_folder,"post_pred_pregCA.png",sep=""), plot=p, width=7, height=8)

```

### Pregnancy samples


```{r}

years=seq(from=2002, to=2024, length=23)

p.post.q<- apply(samples$p, 2, quantile, quantiles)[,1:23]
b.post.q<- apply(samples$b, 2, quantile, quantiles)[,1:23]
y_pr.sim=samples$y_pr_sim
y_pr.s=y_pr[1:23]
y_pr_tot.s=y_pr_tot[1:23]
y_pr.sim.q<- apply(t (y_pr.sim)/y_pr_tot.s, 1, quantile, quantiles, na.rm=TRUE)
y_pr.sim.q
p<-ggplot() +
  geom_ribbon(aes(x=years, ymin=p.post.q[1,], ymax=p.post.q[3,], fill='gray16'), alpha=0.15) +
  geom_line(aes(x=years, y=p.post.q[2,]), col='gray16', alpha=0.5) +
  
  geom_errorbar(aes(x=years, ymin=y_pr.sim.q[1,], ymax=y_pr.sim.q[3,]), alpha=0.35, color="black") +
  geom_linerange(aes(x=years, ymin=y_pr.sim.q[1,], ymax=y_pr.sim.q[3,]), color = "black", alpha=0)+
  geom_point(aes(x=years, y=(y_pr.s)/y_pr_tot.s,  size=y_pr_tot.s), color='black',alpha=1) +
  scale_fill_identity(name='', guide='legend', labels=c('Posterior estimate \n of true value')) +
  scale_size_continuous(name='Sample size', guide='legend', 
breaks=round(seq(min(y_pr_tot[y_pr_tot>0]), max(y_pr_tot), length.out=4))
  ) +
 
  scale_y_continuous(limits=c(0,1)) +
  labs(x='Year', y='Pregnancy rate') +
  theme_classic() +
 
  theme(panel.grid.minor = element_blank(), text = element_text(size=18), legend.position = c(0.47,0.2), label.position="bottom", legend.direction="horizontal") +
  guides(size=guide_legend(title.position="top", label.position = 'bottom'),
         fill='none')

p

ggsave(filename= paste(figure_folder,"post_pred_preg.png"), plot=p, width=7, height=8)

```

### SW harvest 

```{r}
font_size=20
############### Size of the SW hunting bag ######################
years=seq(from=2002, to=2024, length=23)
#source("~/Seals/ringed_seal/ringed_seal/ringed_seal_code/functions/plotting_functions.R")
p=pp_raster(samples$y_hb_sw_sim, as.vector(years), 3, years, as.numeric(y_hb_sw[1:23]), cex=2,
          x_lab='Year', y_lab='Size of Swedish seal harvest', interpolate = FALSE) +
#  scale_x_continuous(limits = c(2014.5, 2022.5), breaks=2015:2022) +
  guides(fill=guide_colorbar(title.position='top', direction='horizontal'),
         colour=guide_legend(override.aes = list(size=3))) +
  theme(legend.position = c(0.35,0.85), legend.spacing.y = unit(0.05, "cm"), 
        legend.background = element_rect(fill = NA), panel.grid.minor = element_blank(), text = element_text(size=font_size))
p
# save plot
ggsave(filename=paste(figure_folder,"post_pred_SW_hb.png",sep=""),plot=p,   width=8, height=8)

```
### FI harvest

```{r}
############### Size of the FI hunting bag ######################

p=pp_raster(samples$y_hb_fi_sim, as.vector(years), 3, years, as.numeric(y_hb_fi), cex=2,
          x_lab='Year', y_lab='Size of Finnish seal harvest', interpolate = FALSE) +
#  scale_x_continuous(limits = c(2014.5, 2022.5), breaks=2015:2022) +
  guides(fill=guide_colorbar(title.position='top', direction='horizontal'),
         colour=guide_legend(override.aes = list(size=3))) +
    #scale_y_continuous(limits=c(0,00)) +
  theme(legend.position ="none", panel.grid.minor = element_blank(), text = element_text(size=font_size))

p
ggsave(filename= paste(figure_folder,"post_pred_FI_hb.png",sep=""),plot=p,   width=8, height=8)

```


# Prior sensitivity analysis


```{r}

# priors 
prior.list = list(
  variable = c("n0", "phi_a_sc", "v0_and_v5", "hunting_and_bycatch_bias", "hunting_effort_sd", "herring_effect", "K", "mu"), 
  index = c(1:8))
lik.list = list(
  data = c("Aerial_observations", "Hunting_bag_sw", "Hunting_bag_fi", "hunting_sample_sw", "hunting_sample_fi", "bycatch_samples", "pregnancy_samples", "reproductive_signs"), 
  index = c(1:8))

# Global sensitivity
powerscale_sensitivity(fit, variable = c("n0", "K", "phi_a_sc", "v0", "v5", "alpha_sc", "beta", "mu"))

# per parameter prior sensitivity
# -------------------------------
# n0 and K
p.dens <- powerscale_plot_dens(fit, variable = "n0", prior_selection = 1) +
  ggdist::stat_halfeye(
    aes(xdist = dist),
    inherit.aes = FALSE,
    slab_alpha=0.5,
    interval_color = "grey",
    point_color =  "grey",
    limits = quantile(as.matrix(fit, par="n0"), p = c(0.01,0.99)),
    data = data.frame(dist = distributional::dist_lognormal(9.8, 0.1))
  )
# K
p.dens2 = powerscale_plot_dens(fit, variable = c("K"), prior_selection = 7) +
  ggdist::stat_halfeye(
    aes(xdist = dist),
    inherit.aes = FALSE,
    slab_alpha=0.5,
    interval_color = "grey",
    point_color =  "grey",
    limits = quantile(as.matrix(fit, par="K"), p = c(0.01,0.99)),
    data = data.frame(dist = distributional::dist_lognormal(11.3,0.3))
  )

p = p.dens + p.dens2
ggsave(filename= paste(figure_folder,"prior_sens_n0_K.png",sep=""),plot=p,   width=18, height=8)


# phi_a and phi_pup
p.dens = powerscale_plot_dens(fit, variable = c("phi_a"), prior_selection = 2) +
  ggdist::stat_halfeye(
    aes(xdist = dist),
    inherit.aes = FALSE,
    slab_alpha=0.5,
    interval_color = "grey",
    point_color =  "grey",
    data = data.frame(dist = distributional::dist_uniform(min = 0.8, max=1))
  )
# phi_pup
p.dens2 = powerscale_plot_dens(fit, variable = c("phi_pup"), prior_selection = 2) +
  ggdist::stat_halfeye(
    aes(x = samples),
    inherit.aes = FALSE,
    slab_alpha=0.5,
    interval_color = "grey",
    point_color =  "grey",
    limits = quantile(as.matrix(fit, par="phi_pup"), p = c(0.01,0.99)),
    data = data.frame(samples = runif(n = 10000, min=0.8, max=1)*runif(n=10000,min=0, max=1))
  )

p = p.dens + p.dens2
ggsave(filename= paste(figure_folder,"prior_sens_phi_a_phi_pup.png",sep=""),plot=p,   width=18, height=8)


# v0 and v5
p.dens = powerscale_plot_dens(fit, variable = c("v0"), prior_selection = 3) +
  ggdist::stat_halfeye(
    aes(xdist = dist),
    inherit.aes = FALSE,
    slab_alpha=0.5,
    interval_color = "grey",
    point_color =  "grey",
    p_limits = quantile(as.matrix(fit, par="v0"), p = c(0.01,0.99)),
    data = data.frame(dist = distributional::dist_cauchy(0,0.2))
  )
# v5
p.dens2 = powerscale_plot_dens(fit, variable = c("v5"), prior_selection = 3)+
  ggdist::stat_halfeye(
    aes(xdist = dist),
    inherit.aes = FALSE,
    slab_alpha=0.5,
    interval_color = "grey",
    point_color =  "grey",
    p_limits = quantile(as.matrix(fit, par="v5"), p = c(0.01,0.99)),
    data = data.frame(dist = distributional::dist_cauchy(0.88,0.2))
  )

p = p.dens + p.dens2
ggsave(filename= paste(figure_folder,"prior_sens_v0_v5.png",sep=""),plot=p,   width=18, height=8)


# b0max and b0min
p.dens = powerscale_plot_dens(fit, variable = c("b0max"), prior_selection = 6) +
  ggdist::stat_halfeye(
    aes(xdist = dist),
    inherit.aes = FALSE,
    slab_alpha=0.5,
    interval_color = "grey",
    point_color =  "grey",
    #p_limits = quantile(as.matrix(fit, par="b0max"), p = c(0.01,0.99)),
    data = data.frame(dist = distributional::dist_uniform(0,1))
  )
# b0min
p.dens2 = powerscale_plot_dens(fit, variable = c("b0min"), prior_selection = 6) +
  ggdist::stat_halfeye(
    aes(x = samples),
    inherit.aes = FALSE,
    slab_alpha=0.5,
    interval_color = "grey",
    point_color =  "grey",
    p_limits = quantile(as.matrix(fit, par="b0min"), p = c(0.01,0.99)),
    data = data.frame(samples = runif(n = 10000, min=0, max=1)*runif(n=10000,min=0, max=1))
  )

p = p.dens + p.dens2
ggsave(filename= paste(figure_folder,"prior_sens_b0max_b0min.png",sep=""),plot=p,   width=18, height=8)


# beta and alpha_sc
p.dens = powerscale_plot_dens(fit, variable = c("beta"), prior_selection = 6) +
  ggdist::stat_halfeye(
    aes(xdist = dist),
    inherit.aes = FALSE,
    slab_alpha=0.5,
    interval_color = "grey",
    point_color =  "grey",
    p_limits = quantile(as.matrix(fit, par="beta"), p = c(0.01,0.99)),
    data = data.frame(dist = distributional::dist_normal(0,3))
  )
# alpha_sc
p.dens2 = powerscale_plot_dens(fit, variable = c("alpha"), prior_selection = 6) +
  ggdist::stat_halfeye(
    aes(x = samples),
    inherit.aes = FALSE,
    slab_alpha=0.5,
    interval_color = "grey",
    point_color =  "grey",
    p_limits = quantile(as.matrix(fit, par="alpha"), p = c(0.01,0.99)),
    data = data.frame(samples = rnorm(n = 10000, mean = 0, sd=sqrt(4))*rnorm(n = 10000, mean = 0, sd=sqrt(3)))
  )

p = p.dens + p.dens2
ggsave(filename= paste(figure_folder,"prior_sens_beta_alpha.png",sep=""),plot=p,   width=18, height=8)


# w and mu
p.dens = powerscale_plot_dens(fit, variable = c("w"), prior_selection = 8) +
  ggdist::stat_halfeye(
    aes(xdist = dist),
    inherit.aes = FALSE,
    slab_alpha=0.5,
    interval_color = "grey",
    point_color =  "grey",
    #p_limits = quantile(as.matrix(fit, par="b0max"), p = c(0.01,0.99)),
    data = data.frame(dist = distributional::dist_uniform(0,1))
  )
# mu
p.dens2 = powerscale_plot_dens(fit, variable = c("mu"), prior_selection = 8) +
  ggdist::stat_halfeye(
    aes(xdist = dist),
    inherit.aes = FALSE,
    slab_alpha=0.5,
    interval_color = "grey",
    point_color =  "grey",
    #p_limits = quantile(as.matrix(fit, par="b0max"), p = c(0.01,0.99)),
    data = data.frame(dist = distributional::dist_beta(32,9))
  )

p = p.dens + p.dens2
ggsave(filename= paste(figure_folder,"prior_sens_w_mu.png",sep=""),plot=p,   width=18, height=8)













```






















# Prior sensitivity analysis with CDFs
```{r}

# priors 
prior.list = list(
  variable = c("n0", "phi_a_sc", "v0_and_v5", "hunting_and_bycatch_bias", "hunting_effort_sd", "herring_effect", "K", "mu"), 
  index = c(1:8))
lik.list = list(
  data = c("Aerial_observations", "Hunting_bag_sw", "Hunting_bag_fi", "hunting_sample_sw", "hunting_sample_fi", "bycatch_samples", "pregnancy_samples", "reproductive_signs"), 
  index = c(1:8))

# Global sensitivity
powerscale_sensitivity(fit, variable = c("n0", "K", "phi_a_sc", "v0", "v5", "alpha_sc", "beta", "mu"))

# per parameter prior sensitivity
# -------------------------------
# n0
#powerscale_sensitivity(fit, variable = c("n0"), prior_selection = 1)
#p.dens = powerscale_plot_dens(fit, variable = c("n0"), prior_selection = 1)
#p.dens <- powerscale_plot_dens(fit, component = "prior", variable = "n0") +
p.dens <- powerscale_plot_dens(fit, variable = "n0", prior_selection = 1) +
  ggdist::stat_halfeye(
    aes(xdist = dist),
    inherit.aes = FALSE,
    slab_alpha=0.5,
    interval_color = "grey",
    point_color =  "grey",
    p_limits = quantile(as.matrix(fit, par="n0"), p = c(0.01,0.99)),
    data = data.frame(dist = distributional::dist_lognormal(9.8, 0.1))
  )
p.ecdf = powerscale_plot_ecdf(fit, variable = c("n0"), prior_selection = 1)
#p.quant = powerscale_plot_quantities(fit, variable = c("n0"), prior_selection = 1)

p = p.dens + p.ecdf
p
ggsave(filename= paste(figure_folder,"prior_sens_n0.png",sep=""),plot=p,   width=18, height=8)

# phi_a_sc
#powerscale_sensitivity(fit, variable = c("phi_a_sc"), prior_selection = 2)
p.dens = powerscale_plot_dens(fit, variable = c("phi_a"), prior_selection = 2) +
  ggdist::stat_halfeye(
    aes(xdist = dist),
    inherit.aes = FALSE,
    slab_alpha=0.5,
    interval_color = "grey",
    point_color =  "grey",
    data = data.frame(dist = distributional::dist_uniform(min = 0.8, max=1))
  )

p.ecdf = powerscale_plot_ecdf(fit, variable = c("phi_a"), prior_selection = 2)
#p.quant = powerscale_plot_quantities(fit, variable = c("phi_a_sc"), prior_selection = 2)

p = p.dens + p.ecdf
p
ggsave(filename= paste(figure_folder,"prior_sens_phi_a.png",sep=""),plot=p,   width=18, height=8)


# v0
#powerscale_sensitivity(fit, variable = c("v0"), prior_selection = 3)
p.dens = powerscale_plot_dens(fit, variable = c("v0"), prior_selection = 3) +
  ggdist::stat_halfeye(
    aes(xdist = dist),
    inherit.aes = FALSE,
    slab_alpha=0.5,
    interval_color = "grey",
    point_color =  "grey",
    p_limits = quantile(as.matrix(fit, par="v0"), p = c(0.01,0.99)),
    data = data.frame(dist = distributional::dist_cauchy(0,0.2))
  )
p.ecdf = powerscale_plot_ecdf(fit, variable = c("v0"), prior_selection = 3)
#p.quant = powerscale_plot_quantities(fit, variable = c("v0"), prior_selection = 3)

p = p.dens + p.ecdf
p
ggsave(filename= paste(figure_folder,"prior_sens_v0.png",sep=""),plot=p,   width=18, height=8)

# v5
#powerscale_sensitivity(fit, variable = c("v5), prior_selection = 3)
p.dens = powerscale_plot_dens(fit, variable = c("v5"), prior_selection = 3)+
  ggdist::stat_halfeye(
    aes(xdist = dist),
    inherit.aes = FALSE,
    slab_alpha=0.5,
    interval_color = "grey",
    point_color =  "grey",
    p_limits = quantile(as.matrix(fit, par="v5"), p = c(0.01,0.99)),
    data = data.frame(dist = distributional::dist_cauchy(0.88,0.2))
  )
p.ecdf = powerscale_plot_ecdf(fit, variable = c("v5"), prior_selection = 3)
#p.quant = powerscale_plot_quantities(fit, variable = c("v5"), prior_selection = 3)

p = p.dens + p.ecdf
p
ggsave(filename= paste(figure_folder,"prior_sens_v5.png",sep=""),plot=p,   width=18, height=8)


# alpha_sc
#powerscale_sensitivity(fit, variable = c("alpha_sc"), prior_selection = 6)
p.dens = powerscale_plot_dens(fit, variable = c("alpha_sc"), prior_selection = 6)+
  ggdist::stat_halfeye(
    aes(xdist = dist),
    inherit.aes = FALSE,
    slab_alpha=0.5,
    interval_color = "grey",
    point_color =  "grey",
    p_limits = quantile(as.matrix(fit, par="alpha_sc"), p = c(0.01,0.99)),
    data = data.frame(dist = distributional::dist_normal(0,4))
  )
p.ecdf = powerscale_plot_ecdf(fit, variable = c("alpha_sc"), prior_selection = 6)
#p.alpha.quant = powerscale_plot_quantities(fit, variable = c("beta"), prior_selection = 6)

p = p.dens + p.ecdf
p
ggsave(filename= paste(figure_folder,"prior_sens_alpha_sc.png",sep=""),plot=p,   width=18, height=8)

# beta
#powerscale_sensitivity(fit, variable = c("beta"), prior_selection = 6)
p.dens = powerscale_plot_dens(fit, variable = c("beta"), prior_selection = 6)
p.ecdf = powerscale_plot_ecdf(fit, variable = c("beta"), prior_selection = 6)
#p.alpha.quant = powerscale_plot_quantities(fit, variable = c("beta"), prior_selection = 6)

p = p.dens + p.ecdf
p
ggsave(filename= paste(figure_folder,"prior_sens_beta.png",sep=""),plot=p,   width=18, height=8)


# K
#powerscale_sensitivity(fit, variable = c("K"), prior_selection = 7)
p.dens = powerscale_plot_dens(fit, variable = c("K"), prior_selection = 7)
p.ecdf = powerscale_plot_ecdf(fit, variable = c("K"), prior_selection = 7)
#p.K.quant = powerscale_plot_quantities(fit, variable = c("K"), prior_selection = 7)

p = p.dens + p.ecdf
p
ggsave(filename= paste(figure_folder,"prior_sens_K.png",sep=""),plot=p,   width=18, height=8)

# mu
#powerscale_sensitivity(fit, variable = c("mu"), prior_selection = 8)
p.dens = powerscale_plot_dens(fit, variable = c("mu"), prior_selection = 8)
p.ecdf = powerscale_plot_ecdf(fit, variable = c("mu"), prior_selection = 8)
#p.mu.quant = powerscale_plot_quantities(fit, variable = c("K"), prior_selection = 8)

p = p.dens + p.ecdf
p
ggsave(filename= paste(figure_folder,"prior_sens_mu.png",sep=""),plot=p,   width=18, height=8)



# Per parameter, specific likelihood sensitivity
# -------------------------------
# n0
p.dens = powerscale_plot_dens(fit, variable = c("n0"), likelihood_selection = 1)
p.ecdf = powerscale_plot_ecdf(fit, variable = c("n0"), likelihood_selection = 1)

p = p.dens + p.ecdf
p
ggsave(filename= paste(figure_folder,"lik_sens_n0.png",sep=""),plot=p,   width=18, height=8)

# phi_a_sc
p.dens = powerscale_plot_dens(fit, variable = c("phi_a_sc"), likelihood_selection = 1)
p.ecdf = powerscale_plot_ecdf(fit, variable = c("phi_a_sc"), likelihood_selection = 1)

p = p.dens + p.ecdf
p
ggsave(filename= paste(figure_folder,"lik_sens_phi_a_sc.png",sep=""),plot=p,   width=18, height=8)

# v0
p.dens = powerscale_plot_dens(fit, variable = c("v0"), likelihood_selection = 1)
p.ecdf = powerscale_plot_ecdf(fit, variable = c("v0"), likelihood_selection = 1)

p = p.dens + p.ecdf
p
ggsave(filename= paste(figure_folder,"lik_sens_v0.png",sep=""),plot=p,   width=18, height=8)

# v5
p.dens = powerscale_plot_dens(fit, variable = c("v5"), likelihood_selection = 1)
p.ecdf = powerscale_plot_ecdf(fit, variable = c("v5"), likelihood_selection = 1)

p = p.dens + p.ecdf
p
ggsave(filename= paste(figure_folder,"lik_sens_v5.png",sep=""),plot=p,   width=18, height=8)

# alpha_sc
p.dens = powerscale_plot_dens(fit, variable = c("alpha_sc"), likelihood_selection = 1)
p.ecdf = powerscale_plot_ecdf(fit, variable = c("alpha_sc"), likelihood_selection = 1)

p = p.dens + p.ecdf
p
ggsave(filename= paste(figure_folder,"lik_sens_alpha_sc.png",sep=""),plot=p,   width=18, height=8)

# beta
p.dens = powerscale_plot_dens(fit, variable = c("beta"), likelihood_selection = 1)
p.ecdf = powerscale_plot_ecdf(fit, variable = c("beta"), likelihoodr_selection = 1)

p = p.dens + p.ecdf
p
ggsave(filename= paste(figure_folder,"lik_sens_beta.png",sep=""),plot=p,   width=18, height=8)


# alpha_sc
p.dens = powerscale_plot_dens(fit, variable = c("alpha_sc"), likelihood_selection = c(7,8))
p.ecdf = powerscale_plot_ecdf(fit, variable = c("alpha_sc"), likelihood_selection = c(7,8))

p = p.dens + p.ecdf
p
ggsave(filename= paste(figure_folder,"lik78_sens_alpha_sc.png",sep=""),plot=p,   width=18, height=8)

# beta
p.dens = powerscale_plot_dens(fit, variable = c("beta"), likelihood_selection = c(7,8))
p.ecdf = powerscale_plot_ecdf(fit, variable = c("beta"), likelihoodr_selection = c(7,8))

p = p.dens + p.ecdf
p
ggsave(filename= paste(figure_folder,"lik78_sens_beta.png",sep=""),plot=p,   width=18, height=8)

# K
p.dens = powerscale_plot_dens(fit, variable = c("K"), likelihood_selection = 1)
p.ecdf = powerscale_plot_ecdf(fit, variable = c("K"), likelihood_selection = 1)

p = p.dens + p.ecdf
p
ggsave(filename= paste(figure_folder,"lik_sens_K.png",sep=""),plot=p,   width=18, height=8)

# mu
p.dens = powerscale_plot_dens(fit, variable = c("mu"), likelihood_selection = 1)
p.ecdf = powerscale_plot_ecdf(fit, variable = c("mu"), likelihood_selection = 1)

p = p.dens + p.ecdf
p
ggsave(filename= paste(figure_folder,"lik_sens_mu.png",sep=""),plot=p,   width=18, height=8)

# mu
p.dens = powerscale_plot_dens(fit, variable = c("mu"), likelihood_selection = c(2,3))
p.ecdf = powerscale_plot_ecdf(fit, variable = c("mu"), likelihood_selection = c(2,3))

p = p.dens + p.ecdf
p
ggsave(filename= paste(figure_folder,"lik23_sens_mu.png",sep=""),plot=p,   width=18, height=8)




```

